---
title: "Finalprojsurvey"
author: "Sikha"
output:
  word_document: default
  html_document: default
---
## Set the directory
```{r}
setwd("C:/Users/sikha/Desktop/R-SIKHA/Final Project")
```

## Libraryran
```{r}

library(eeptools)
library(dplyr)
library(data.table)
library(ggplot2)
library(sandwich)
library(msm)

```

#loading the data
```{r}

hrdata=read.table("Transaction-HR data FY11-FY14.txt",
                   sep="\t",
                   header=TRUE,
                   fill=FALSE,
                 strip.white=TRUE)

library(readxl)
Training12=read_excel("t12model1.xlsx")
Training13=read_excel("t13model1.xlsx")
store=read.csv("Store attributes.csv", sep=",")
survey=read.csv("Survey data.csv")
```
# Merging survey data with hrdata
```{r}
#changing 'No=2 to No=0'and 'do not recall=9 to do not recall=NA' for columns7,8,19
#survey$greetedbinary<-ifelse(survey$greetedbinary==9,NA,ifelse(survey$greetedbinary==2,0,1))
#survey$jcdiscussedcreditoptionsbinary<-ifelse(survey$jcdiscussedcreditoptionsbinary==9,NA,ifelse(#survey$jcdiscussedcreditoptionsbinary==2,0,1))
#survey$informedeventbinary<- ifelse(survey$informedeventbinary==2,0,1)

#creating survey score(total of scores per transaction)
#survey$surveyscore<- rowSums(survey[7:19],na.rm=TRUE)

survey$servicecompetency<-rowMeans(survey[,c("sh1","sh2","sh3","sh4","sh5","pressure")],na.rm=TRUE)
survey$productcompetency<-rowMeans(survey[,c("sc1","sc2","sc3","sc4")],na.rm=TRUE)

#renaming "purchase transaction amount" to "net_purchase_amount"
colnames(survey)[colnames(survey)=="purchasetransactionamount"]<-"net_purchase_amount"

library(dplyr)
# checking for duplicate transactions per year
uniqueTransHRdata<-distinct(hrdata)#there were 76,693 duplicate rows.

## Merging Trans HR data with survey
HRdataSurvey<- merge(uniqueTransHRdata, survey, by=c("customer_id","net_purchase_amount","transaction_id","purchase_date","store_number"), all=TRUE)

#Merge added extra 413 rows. Removing them.
HRdataSurvey<-HRdataSurvey[!is.na(HRdataSurvey$sales_assoc_1), ]

## Removing extra data from HR data that didn't have survey scores.
HRdataSurvey1<-HRdataSurvey
HRdataSurvey12<-HRdataSurvey1[!is.na(HRdataSurvey1$productcompetency), ]
```
#distinct  sales associate dataset from HRdataSurvey12
```{r}
subsetHRdataS<- HRdataSurvey12[c("sales_assoc_1","SA_gender","SA_AssignmentCategory","SA_MartialStatus","SA_Dependent")]
library(dplyr)
uniqueHRdataS<-distinct(subsetHRdataS)

#creating dummy variables for gender of customers
HRdataSurvey12$female<-ifelse(HRdataSurvey12$gender=="F",1,0)
HRdataSurvey12$male<-ifelse(HRdataSurvey12$gender=="M",1,0)

#creating dummy variable for home owner code
HRdataSurvey12$homeowners<-ifelse(HRdataSurvey12$homeowner_code=="O",1,0)

#creating dummy variable for child of a customer
HRdataSurvey12$child<-ifelse(HRdataSurvey12$child=="Y",1,0)

monthlyHRaggregate12=HRdataSurvey12 %>% group_by(sales_assoc_1,month_index,store_number) %>% summarise(year=mean(year),monthlysales=sum(net_purchase_amount),monthlyreturn=sum(return),meanAgeBand=mean(age_band),meanIncomeCode=mean(est_income_code),MeanFemales=mean(female), MeanMales=mean(male),SA_serviceyears=mean(SA_YearsofService),SA_rateofPay=mean(SA_RateofPay),meanChild=mean(child),meanHomeowners=mean(homeowners),count=n(),meanPurchaseBasketSize=mean(purchasebasketsize),productcompetency=mean(productcompetency),servicecompetency=mean(servicecompetency))

#merging MonthlyHRaggregate and uniqueHRdata
FinalHRdata123<- merge(monthlyHRaggregate12, uniqueHRdataS, by=c("sales_assoc_1"), all=TRUE)

#renaming count variable as monthlypurchases
colnames(FinalHRdata123)[colnames(FinalHRdata123)=="count"]<-"monthlyPurchases"

#Adding fiscal year column in Final HR data
FinalHRdata123$month_num <- ((FinalHRdata123$month_index+7) %% 12)
FinalHRdata123$month_num<- ifelse(FinalHRdata123$month_num==0,12,FinalHRdata123$month_num)
FinalHRdata123$fiscalyear<-ifelse(FinalHRdata123$month_num==8,(FinalHRdata123$year+1),ifelse(FinalHRdata123$month_num==9,(FinalHRdata123$year+1),ifelse(FinalHRdata123$month_num==10,(FinalHRdata123$year+1),ifelse(FinalHRdata123$month_num==11,(FinalHRdata123$year+1),ifelse(FinalHRdata123$month_num==12,(FinalHRdata123$year+1),FinalHRdata123$year)))))
```

```{r}
##Merging training data with FinalHRdataSurvey12
Model2Trainingdata=read_excel("sptraining.xlsx")

#renaming the column heads
colnames(Model2Trainingdata)[colnames(Model2Trainingdata)=="Warranties"]<-"Warranty"
colnames(Model2Trainingdata)[colnames(Model2Trainingdata)=="Sp. Events"]<-"Spec. Ev."
colnames(Model2Trainingdata)[colnames(Model2Trainingdata)=="EID"]<-"sales_assoc_1"

#creating a subset of Model2Trainingdata which doesnot include store#,state,assignment category. Because this info. is present in HR data.so dont want redundant data.
subsetTraining<-Model2Trainingdata[c("Status","sales_assoc_1","Job Name","Start Date","Rehire","Warranty","Credit","Spec. Ev.","Celebrity Brand","Celebration","Watches","Color","Service & Selling","fiscalyear","ptraining","straining")]

#Merging SubsetTraining with FinalHRdata
SurveyMod<-merge(FinalHRdata123, subsetTraining, by=c("sales_assoc_1", "fiscalyear"),all=TRUE)

## Removing 126 extra rows from SurveyMod

SurveyMod2<-SurveyMod[!is.na(SurveyMod$month_index), ]
```
## Merging SurveyMod2 with Store attributes

```{r}
SurveyMod3 <-merge(SurveyMod2, store, by=c("store_number"), all=TRUE)

## Removing 1 extra rows from SurveyMod3
SurveyMod4<-SurveyMod3[!is.na(SurveyMod3$sales_assoc_1), ]

#creating dummy variables for gender of customers
SurveyMod4$SA_gender1<-ifelse(SurveyMod4$SA_gender=="F",1,0)
SurveyMod4$SA_Dependent<-ifelse(SurveyMod4$SA_Dependent=="Yes",1,0)
SurveyMod4$ST <- factor(SurveyMod4$ST, levels = c("AR", "AZ","FL","IA","IL","IN","MA","MD","MI","OK","PA","PR","SD","TX"," VA","WA" ))

#Dividing survey scores into three categories.
#SurveyMod4$PercievedCompetency<-ifelse(SurveyMod4$meanSurveyScore>=35,"Good",ifelse(SurveyMod4$meanSurveyScore>18,"OK","Bad"))
#SurveyMod4$training<-ifelse(SurveyMod4$TrainingCompleted>0,1,0)
#SurveyMod4$TrainingCompleted<-ifelse(is.na(SurveyMod4$TrainingCompleted),0,SurveyMod4$TrainingComplete)
SurveyMod5  = na.omit(SurveyMod4, cols= "meanAgeBand")

```
## Check Multicollineary
```{r}
#Multicollinearity
#Error in vif(df1) : object 'df1' not found
##library(VIF)
##library(usdm)

##df1=data.frame(Mod4$ptraining,SurveyMod4$straining,SurveyMod4$SA_serviceyears,SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales,SurveyMod4$MallSalesSF,SurveyMod4$fiscalyear)

##cor(df1)
##vif(df1)

```
# 1st Model
```{r}
logmonthlysales<-log(Mod1data$monthlysales+1)
factorJobName<-factor(Mod1data$`Job Name`)

Model1<-lm(logmonthlysales~training+meanAgeBand+meanIncomeCode+MeanFemales+MeanMales+SA_serviceyears+SA_rateofPay+meanChild+meanHomeowners+factor(month_num)+factor(fiscalyear)+factor(ST)+factor(MallGrade)+TotalCases, data=Mod1data)
print(summary(Model1))




ModelPR1<-lm(SurveyMod4$productcompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+factor(SurveyMod4$MallGrade)+SurveyMod4$MallSalesSF+SurveyMod4$MajorCompetitorPresent+SurveyMod4$fiscalyear +factor(SurveyMod4$month_num))
summary(ModelPR1)


coooolll
#Multicollinearity
library(VIF)
library(usdm)

df1=data.frame(Mod1data$training,Mod1data$meanAgeBand,Mod1data$meanIncomeCode,Mod1data$MeanFemales,Mod1data$MeanMales,Mod1data$SA_serviceyears,Mod1data$SA_rateofPay,Mod1data$meanChild,Mod1data$meanHomeowners, Mod1data$month_num,  Mod1data$TotalCases, Mod1data$fiscalyear, Mod1data$MallSalesSF,Mod1data$StoreSqFt)

vif(df1)     
cor(df1)


```{r}
library(usdm)
library(VIF)
dfS1=data.frame(SurveyMod4$ptraining+SurveyMod4$straining,SurveyMod4$SA_serviceyears,SurveyMod4$meanIncomeCode, SurveyMod4$MeanFemales, SurveyMod4$MeanMales, SurveyMod4$MallSalesSF SurveyMod4$SA_rateofPay,SurveyMod4$meanChild,SurveyMod4$meanHomeowners, SurveyMod4$month_num, SurveyMod4$SA_serviceyears, SurveyMod4$TotalCases, SurveyMod4$fiscalyear, SurveyMod4$sales_assoc_1, SurveyMod4$store_number,SurveyMod4$MallSalesSF,SurveyMod4$StoreSqFt,SurveyMod4$MeanMales, SurveyMod4$monthlyreturn, SurveyMod4$SA_gender1) 

vif(dfS1)
cor(dfS1)
SurveyMod4$productcompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+factor(SurveyMod4$MallGrade)+SurveyMod4$MallSalesSF+SurveyMod4$MajorCompetitorPresent+SurveyMod4$fiscalyear +factor(SurveyMod4$month_num))


dfS1=data.frame(SurveyMod4$TrainingCompleted,SurveyMod4$monthlysales,SurveyMod4$monthlyreturn,SurveyMod4$SA_gender1,SurveyMod4$meanAgeBand,SurveyMod4$meanIncomeCode,SurveyMod4$month_num,SurveyMod4$SA_serviceyears,SurveyMod4$SA_rateofPay,SurveyMod4$MallSalesSF, SurveyMod4$MeanFemales, SurveyMod4$MeanMales)

vif(dfS1)
cor(dfS1)
```


```{r}
## Compare alternative product models

library(lmtest)
#Initial Model
ModelPR1<-lm(SurveyMod4$productcompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+factor(SurveyMod4$MallGrade)+SurveyMod4$MallSalesSF+SurveyMod4$MajorCompetitorPresent+SurveyMod4$fiscalyear +factor(SurveyMod4$month_num))
summary(ModelPR1)##p-value: 0.4264>.05, hence insignificant

###Model with SA_rateofPay 
ModelPR2<-lm(SurveyMod4$productcompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+factor(SurveyMod4$MallGrade)+SurveyMod4$MallSalesSF+SurveyMod4$MajorCompetitorPresent+SurveyMod4$fiscalyear+factor(SurveyMod4$month_num)+SurveyMod4$SA_rateofPay)
summary(ModelPR2)##p-value: 0.4601>.05, hence insignificant

anova(ModelPR1, ModelPR2, test = "Chisq") #Chi Square test shows that  ModelPR1 is better than ModelPR2

###Model with factor(SurveyMod4$`Job Name`) 
ModelPR3<-lm(SurveyMod4$productcompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+factor(SurveyMod4$MallGrade)+SurveyMod4$MallSalesSF+SurveyMod4$MajorCompetitorPresent+SurveyMod4$fiscalyear+factor(SurveyMod4$month_num)+factor(SurveyMod4$`Job Name`))
summary(ModelPR3)

anova(ModelPR1, ModelPR3, test = "Chisq") #Chi Square test shows that  ModelPR1 is better than ModelPR3

###Model with SurveyMod4$meanChild
ModelPR4<-lm(SurveyMod4$productcompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+factor(SurveyMod4$MallGrade)+SurveyMod4$MallSalesSF+SurveyMod4$MajorCompetitorPresent+SurveyMod4$fiscalyear +factor(SurveyMod4$month_num)+ SurveyMod4$meanChild)
summary(ModelPR4)

anova(ModelPR1, ModelPR4, test = "Chisq") #Chi Square test shows that  ModelPR1 is better than ModelPR4

###Model with SurveyMod4$meanPurchaseBasketSize
ModelPR5<-lm(SurveyMod4$productcompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+factor(SurveyMod4$MallGrade)+SurveyMod4$MallSalesSF+SurveyMod4$MajorCompetitorPresent+SurveyMod4$fiscalyear +factor(SurveyMod4$month_num)+ SurveyMod4$meanPurchaseBasketSize)

summary(ModelPR5)

anova(ModelPR1, ModelPR5, test = "Chisq") #Chi Square test shows that  ModelPR5 is better than ModelPR1

###Model with SurveyMod4$monthlysales
ModelPR6<-lm(SurveyMod4$productcompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+factor(SurveyMod4$MallGrade)+SurveyMod4$MallSalesSF+SurveyMod4$MajorCompetitorPresent+SurveyMod4$fiscalyear +factor(SurveyMod4$month_num)+ SurveyMod4$meanPurchaseBasketSize+ SurveyMod4$monthlysales)
summary(ModelPR6)

anova(ModelPR5, ModelPR6, test = "Chisq") #Chi Square test shows that  ModelPR5 is better than ModelPR6

###Model with SurveyMod4$monthlyreturn
ModelPR7<-lm(SurveyMod4$productcompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+factor(SurveyMod4$MallGrade)+SurveyMod4$MallSalesSF+SurveyMod4$MajorCompetitorPresent+SurveyMod4$fiscalyear +factor(SurveyMod4$month_num)+ SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn)
summary(ModelPR7)

anova(ModelPR5, ModelPR7, test = "Chisq") #Chi Square test shows that  ModelPR7 is better than ModelPR5

###Model with SurveyMod4$monthlyPurchases  
ModelPR8<-lm(SurveyMod4$productcompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+factor(SurveyMod4$MallGrade)+SurveyMod4$MallSalesSF+SurveyMod4$MajorCompetitorPresent+SurveyMod4$fiscalyear +factor(SurveyMod4$month_num)+ SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn+SurveyMod4$monthlyPurchases)
summary(ModelPR8)

anova(ModelPR7, ModelPR8, test = "Chisq") #Chi Square test shows that  ModelPR7 is better than ModelPR8


###Model with SurveyMod4$meanHomeowners
ModelPR9<-lm(SurveyMod4$productcompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+factor(SurveyMod4$MallGrade)+SurveyMod4$MallSalesSF+SurveyMod4$MajorCompetitorPresent+SurveyMod4$fiscalyear +factor(SurveyMod4$month_num)+ SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn+SurveyMod4$meanHomeowners)
summary(ModelPR9)

anova(ModelPR7, ModelPR9, test = "Chisq")#Chi Square test shows that  ModelPR7 is better than ModelPR9

###Model with SurveyMod4$TotalCases
ModelPR10<-lm(SurveyMod4$productcompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+factor(SurveyMod4$MallGrade)+SurveyMod4$MallSalesSF+SurveyMod4$MajorCompetitorPresent+SurveyMod4$fiscalyear +factor(SurveyMod4$month_num)+ SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn+SurveyMod4$TotalCases)
summary(ModelPR10)

anova(ModelPR7, ModelPR10, test = "Chisq")#Chi Square test shows that  ModelPR7 is better than ModelPR10

###Model with SurveyMod4$PadCount
ModelPR11<-lm(SurveyMod4$productcompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+factor(SurveyMod4$MallGrade)+SurveyMod4$MallSalesSF+SurveyMod4$MajorCompetitorPresent+SurveyMod4$fiscalyear +factor(SurveyMod4$month_num)+ SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn+SurveyMod4$PadCount)
summary(ModelPR11)

anova(ModelPR7, ModelPR11, test = "Chisq")#Chi Square test shows that  ModelPR7 is better than ModelPR11

###Model without SurveyMod4$fiscalyear 
ModelPR12<-lm(SurveyMod4$productcompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+factor(SurveyMod4$MallGrade)+SurveyMod4$MallSalesSF+SurveyMod4$MajorCompetitorPresent+factor(SurveyMod4$month_num)+ SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn)
summary(ModelPR12)

anova(ModelPR7, ModelPR12, test = "Chisq") #Chi Square test shows that  ModelPR12 is better than ModelPR7

####Model without factor(SurveyMod4$MallGrade) 
ModelPR13<-lm(SurveyMod4$productcompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+SurveyMod4$MallSalesSF+SurveyMod4$MajorCompetitorPresent+factor(SurveyMod4$month_num)+ SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn)
summary(ModelPR13)

anova(ModelPR12, ModelPR13, test = "Chisq")#Chi Square test shows that  ModelPR13 is better than ModelPR12


####Model without SurveyMod4$MallSalesSF 
ModelPR14<-lm(SurveyMod4$productcompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+SurveyMod4$MajorCompetitorPresent+factor(SurveyMod4$month_num)+ SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn)
summary(ModelPR14)

anova(ModelPR13, ModelPR14, test = "Chisq")#Chi Square test shows that  ModelPR14 is better than ModelPR13

####Model without SurveyMod4$MajorCompetitorPresent 
ModelPR15<-lm(SurveyMod4$productcompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+factor(SurveyMod4$month_num)+SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn)
summary(ModelPR15)

anova(ModelPR14, ModelPR15, test = "Chisq")#Chi Square test shows that  ModelPR15 is better than ModelPR14


####Model without factor(SurveyMod4$month_num) 
ModelPR16<-lm(SurveyMod4$productcompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn)
summary(ModelPR16)

anova(ModelPR15, ModelPR16, test = "Chisq")#Chi Square test shows that  ModelPR16 is better than ModelPR15

####Model with SA_gender1
ModelPR17<-lm(SurveyMod4$productcompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn+ SurveyMod4$SA_gender1)
summary(ModelPR17)


anova(ModelPR16, ModelPR17, test = "Chisq")# Model16#Chi Square test shows that  ModelPR16 is better than ModelPR17

####Model with SA_marital status
ModelPR18<-lm(SurveyMod4$productcompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn+ SurveyMod4$SA_MartialStatus)
summary(ModelPR18)

anova(ModelPR16, ModelPR18, test = "Chisq")# Model16#Chi Square test shows that  ModelPR16 is better than ModelPR18

###Though Model 16 onwards p value of the model is significant, but adjusted R^2 is  very low and   Key independent variables are insignificant

####So final OLS Model 16

ModelPR16<-lm(SurveyMod4$productcompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn)
summary(ModelPR16)


```
#Test for Heteroskedasticity
```{r}

library(msm)
library(lmtest)
gqtest(ModelPR16)#p-value is significant.GQ test result says that there is heteroskedasticity
bptest(ModelPR16)# p-value is insignificant. So, there is heteroskedasticity.
library(sandwich)
library(foreign)
coeftest(ModelPR16, vcov = vcovHC(ModelPR16, "HC1"))#So, generated robust standard errors however, insights did not change


```

```{r}
####Endogenty 

library(AER)
library(foreign)

ModelPR21<-ivreg(SurveyMod4$productcompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+SurveyMod4$fiscalyear +SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn|SurveyMod4$SA_gender1+SurveyMod4$SA_MartialStatus+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+SurveyMod4$fiscalyear +SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn)
summary(ModelPR21,diagnostics = TRUE)
##for Model PR23 , 1)F-Statistics of the instruments <10, therefore instrument relevance assumption not met, Since one of the two assumptions  not met; therefore Wu-Hausman is valid

ModelPR23<-ivreg(SurveyMod4$productcompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+SurveyMod4$fiscalyear+SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn|SurveyMod4$SA_Dependent+SurveyMod4$SA_MartialStatus+SurveyMod4$SA_AssignmentCategory+SurveyMod4$SA_serviceyears+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+SurveyMod4$fiscalyear+SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn)
summary(ModelPR23,diagnostics = TRUE)

##for Model PR23 , 1)F-Statistics of the instruments <10, therefore instrument relevance assumption not met, Sinc one of the two assumptions  not met therefore Wu-Hausman is valid

ModelPR24<-ivreg(SurveyMod4$productcompetency~SurveyMod4$ptraining+SurveyMod4$straining+SurveyMod4$SA_serviceyears+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn|SurveyMod4$SA_Dependent+SurveyMod4$SA_MartialStatus+SurveyMod4$SA_AssignmentCategory+SurveyMod4$SA_serviceyears+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn)
summary(ModelPR24,diagnostics = TRUE)
##for Model PR23 , 1)F-Statistics of the instruments <10, therefore instrument relevance assumption not met, Sinc one of the two assumptions  not met therefore Wu-Hausman is valid

ModelPR25<-ivreg(SurveyMod4$productcompetency~SurveyMod4$ptraining+SurveyMod4$straining+SurveyMod4$SA_serviceyears+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn|SurveyMod4$MallSalesSF+SurveyMod4$SA_MartialStatus+SurveyMod4$SA_AssignmentCategory+SurveyMod4$SA_serviceyears+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn)
summary(ModelPR25,diagnostics = TRUE)
##for Model PR23 , 1)F-Statistics of the instruments <10, therefore instrument relevance assumption not met, Sinc one of the two assumptions  not met therefore Wu-Hausman is valid

```


## Check Multicollineary
```{r}
## Check Multicollineary
```{r}
#Multicollinearity
#Error in vif(df1) : object 'df1' not found
##library(VIF)
##library(usdm)

##df1=data.frame(Mod4$ptraining,SurveyMod4$straining,SurveyMod4$SA_serviceyears,SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales,SurveyMod4$MallSalesSF,SurveyMod4$fiscalyear)

##cor(df1)
##vif(df1)

```

```{r}
## Compare alternative service models


library(lmtest)
library(usdm)


#Initial Model


ModelSR1<-lm(SurveyMod4$servicecompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+factor(SurveyMod4$MallGrade)+SurveyMod4$MallSalesSF+SurveyMod4$MajorCompetitorPresent+SurveyMod4$fiscalyear +factor(SurveyMod4$month_num))
summary(ModelSR1)

###Model with SA_rateofPay 
ModelSR2<-lm(SurveyMod4$servicecompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+factor(SurveyMod4$MallGrade)+SurveyMod4$MallSalesSF+SurveyMod4$MajorCompetitorPresent+SurveyMod4$fiscalyear+factor(SurveyMod4$month_num)+SurveyMod4$SA_rateofPay)
summary(ModelSR2)


anova(ModelSR1, ModelSR2, test = "Chisq") #Chi Square test shows that  ModelSR1 is better than ModelSR2

###Model with factor(SurveyMod4$`Job Name`) 
ModelSR3<-lm(SurveyMod4$servicecompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+factor(SurveyMod4$MallGrade)+SurveyMod4$MallSalesSF+SurveyMod4$MajorCompetitorPresent+SurveyMod4$fiscalyear+factor(SurveyMod4$month_num)+factor(SurveyMod4$`Job Name`))
summary(ModelSR3)

anova(ModelSR1, ModelSR3, test = "Chisq") # #Chi Square test shows that  ModelSR1 is better than ModelSR2

###Model with SurveyMod4$meanChild
ModelSR4<-lm(SurveyMod4$servicecompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+factor(SurveyMod4$MallGrade)+SurveyMod4$MallSalesSF+SurveyMod4$MajorCompetitorPresent+SurveyMod4$fiscalyear +factor(SurveyMod4$month_num)+ SurveyMod4$meanChild)
summary(ModelSR4)

anova(ModelSR1, ModelSR4, test = "Chisq") # #Chi Square test shows that  ModelSR1 is better than ModelSR4

###Model with SurveyMod4$meanPurchaseBasketSize
ModelSR5<-lm(SurveyMod4$servicecompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+factor(SurveyMod4$MallGrade)+SurveyMod4$MallSalesSF+SurveyMod4$MajorCompetitorPresent+SurveyMod4$fiscalyear +factor(SurveyMod4$month_num)+ SurveyMod4$meanPurchaseBasketSize)
summary(ModelSR5)

anova(ModelSR1, ModelSR5, test = "Chisq") #Chi Square test shows that  ModelSR5is better than ModelSR1

###Model with SurveyMod4$monthlysales
ModelSR6<-lm(SurveyMod4$servicecompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+factor(SurveyMod4$MallGrade)+SurveyMod4$MallSalesSF+SurveyMod4$MajorCompetitorPresent+SurveyMod4$fiscalyear +factor(SurveyMod4$month_num)+ SurveyMod4$meanPurchaseBasketSize+ SurveyMod4$monthlysales)
summary(ModelSR6)

anova(ModelSR5, ModelSR6, test = "Chisq") #Chi Square test shows that  ModelSR5is better than ModelSR6

###Model with SurveyMod4$monthlyreturn
ModelSR7<-lm(SurveyMod4$servicecompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+factor(SurveyMod4$MallGrade)+SurveyMod4$MallSalesSF+SurveyMod4$MajorCompetitorPresent+SurveyMod4$fiscalyear +factor(SurveyMod4$month_num)+ SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn)
summary(ModelSR7)

anova(ModelSR5, ModelSR7, test = "Chisq") #Chi Square test shows that  ModelSR7is better than ModelSR5

###Model with SurveyMod4$monthlyPurchases  
ModelSR8<-lm(SurveyMod4$servicecompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+factor(SurveyMod4$MallGrade)+SurveyMod4$MallSalesSF+SurveyMod4$MajorCompetitorPresent+SurveyMod4$fiscalyear +factor(SurveyMod4$month_num)+ SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn+SurveyMod4$monthlyPurchases)
summary(ModelSR8)

anova(ModelSR7, ModelSR8, test = "Chisq") # #Chi Square test shows that  ModelSR7is better than ModelSR8

library(lmtest)

###Model with SurveyMod4$meanHomeowners
ModelSR9<-lm(SurveyMod4$servicecompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+factor(SurveyMod4$MallGrade)+SurveyMod4$MallSalesSF+SurveyMod4$MajorCompetitorPresent+SurveyMod4$fiscalyear +factor(SurveyMod4$month_num)+ SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn+SurveyMod4$meanHomeowners)
summary(ModelSR9)

anova(ModelSR7, ModelSR9, test = "Chisq")##Chi Square test shows that  ModelSR7is better than ModelSR9

###Model with SurveyMod4$TotalCases
ModelSR10<-lm(SurveyMod4$servicecompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+factor(SurveyMod4$MallGrade)+SurveyMod4$MallSalesSF+SurveyMod4$MajorCompetitorPresent+SurveyMod4$fiscalyear +factor(SurveyMod4$month_num)+ SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn+SurveyMod4$TotalCases)
summary(ModelSR10)

anova(ModelSR7, ModelSR10, test = "Chisq")###Chi Square test shows that  ModelSR7is better than ModelSR10

###Model with SurveyMod4$PadCount
ModelSR11<-lm(SurveyMod4$servicecompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+factor(SurveyMod4$MallGrade)+SurveyMod4$MallSalesSF+SurveyMod4$MajorCompetitorPresent+SurveyMod4$fiscalyear +factor(SurveyMod4$month_num)+ SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn+SurveyMod4$PadCount)
summary(ModelSR11)

anova(ModelSR7, ModelSR11, test = "Chisq")##Chi Square test shows that  ModelSR7is better than ModelSR11

###Model without SurveyMod4$fiscalyear 
ModelSR12<-lm(SurveyMod4$servicecompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+factor(SurveyMod4$MallGrade)+SurveyMod4$MallSalesSF+SurveyMod4$MajorCompetitorPresent+factor(SurveyMod4$month_num)+ SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn)
summary(ModelSR12)

library(lmtest)
anova(ModelSR7, ModelSR12, test = "Chisq") ##Chi Square test shows that  ModelSR12is better than ModelSR7


####Model without factor(SurveyMod4$MallGrade) 
ModelSR13<-lm(SurveyMod4$servicecompetency~SurveyMod4$ptraining+SurveyMod4$straining+ SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+SurveyMod4$MallSalesSF+SurveyMod4$MajorCompetitorPresent+factor(SurveyMod4$month_num)+ SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn)
summary(ModelSR13)

anova(ModelSR12, ModelSR13, test = "Chisq")##Chi Square test shows that  ModelSR13is better than ModelSR12

####Model without SurveyMod4$MallSalesSF 
ModelSR14<-lm(SurveyMod4$servicecompetency~SurveyMod4$ptraining+SurveyMod4$straining+SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+SurveyMod4$MajorCompetitorPresent+factor(SurveyMod4$month_num)+ SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn)
summary(ModelSR14)

anova(ModelSR13, ModelSR14, test = "Chisq")##Chi Square test shows that  ModelSR14is better than ModelSR13

####Model without SurveyMod4$MajorCompetitorPresent 
ModelSR15<-lm(SurveyMod4$servicecompetency~SurveyMod4$ptraining+SurveyMod4$straining+SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+factor(SurveyMod4$month_num)+SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn)

anova(ModelSR14, ModelSR15, test = "Chisq")##Chi Square test shows that  ModelSR15is better than ModelSR14


####Model without factor(SurveyMod4$month_num) 
ModelSR16<-lm(SurveyMod4$servicecompetency~SurveyMod4$ptraining+SurveyMod4$straining+SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn)
summary(ModelSR16)

anova(ModelSR15, ModelSR16, test = "Chisq")##Chi Square test shows that  ModelSR16is better than ModelSR15

####Model with SA_gender1
ModelSR17<-lm(SurveyMod4$servicecompetency~SurveyMod4$ptraining+SurveyMod4$straining+SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn+SurveyMod4$SA_gender1)
summary(ModelSR17)

anova(ModelSR16, ModelSR17, test = "Chisq")##Chi Square test shows that  ModelSR16is better than ModelSR17

###Though Model 16 onwards p value of the model is significant, but adjusted R^2 is  very low and   Key independent variables are insignificant
##Final OLS Model
ModelSR16<-lm(SurveyMod4$servicecompetency~SurveyMod4$ptraining+SurveyMod4$straining+SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn)
summary(ModelSR16)



```
#Test for Heteroskedasticity
```{r}

library(msm)
library(lmtest)
gqtest(ModelSR16)#p-value is significant.GQ test result says that there is heteroskedasticity
bptest(ModelSR16)# p-value is insignificant. So, there is heteroskedasticity.
library(sandwich)
library(foreign)
coeftest(ModelSR16, vcov = vcovHC(ModelSR16, "HC1"))#So, need to use robust standard errors.
summary(ModelSR16)

```

```{r}
###ENDOGENITY--SERVICE MODEL

library(AER)
library(foreign)
ModelSR21<-ivreg(SurveyMod4$servicecompetency~SurveyMod4$ptraining+SurveyMod4$straining+SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn|SurveyMod4$SA_gender1+SurveyMod4$SA_MartialStatus+SurveyMod4$SA_serviceyears+SurveyMod4$SA_AssignmentCategory+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn)
summary(ModelSR21,diagnostics = TRUE)

##for Model SR21 , 1)F-Statistics of the instruments <10, therefore instrument relevance assumption not met, Sinc one of the two assumptions  not met therefore Wu-Hausman is valid

ModelSR22<-ivreg(SurveyMod4$servicecompetency~SurveyMod4$ptraining+SurveyMod4$straining+SurveyMod4$SA_serviceyears+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn|SurveyMod4$SA_gender1+SurveyMod4$SA_MartialStatus+SurveyMod4$SA_AssignmentCategory+SurveyMod4$SA_serviceyears+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn)
summary(ModelSR22,diagnostics = TRUE)
##for Model SR22 , 1)F-Statistics of the instruments <10, therefore instrument relevance assumption not met, Sinc one of the two assumptions  not met therefore Wu-Hausman is valid

ModelSR23<-ivreg(SurveyMod4$servicecompetency~SurveyMod4$ptraining+SurveyMod4$straining+SurveyMod4$SA_serviceyears+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn|SurveyMod4$SA_Dependent+SurveyMod4$SA_MartialStatus+SurveyMod4$SA_AssignmentCategory+SurveyMod4$SA_serviceyears+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn)
summary(ModelSR23,diagnostics = TRUE)

##for Model SR22 , 1)F-Statistics of the instruments <10, therefore instrument relevance assumption not met, Sinc one of the two assumptions  not met therefore Wu-Hausman is valid

ModelSR24<-ivreg(SurveyMod4$servicecompetency~SurveyMod4$ptraining+SurveyMod4$straining+SurveyMod4$SA_serviceyears+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn|SurveyMod4$SA_Dependent+SurveyMod4$MallSalesSF+SurveyMod4$SA_AssignmentCategory+SurveyMod4$SA_serviceyears+SurveyMod4$meanIncomeCode+SurveyMod4$MeanFemales+SurveyMod4$MeanMales+factor(SurveyMod4$ST)+SurveyMod4$meanPurchaseBasketSize+SurveyMod4$monthlyreturn)
summary(ModelSR24,diagnostics = TRUE)

```

